Avoiding global deforestation by taxing land in agricultural production: The implications for global markets

### 2024-03-14 paper.Rmd
Update paper.Rmd

---
title: "Avoiding global deforestation by taxing land in agricultural production: The implications for global markets"
date: "`r format(Sys.time(), '%B %d, %Y')`"
author: "Eric C. Davis, Maros Ivanic, and Brent Sohngen"
output: 
  bookdown::pdf_document2:
    keep_tex: TRUE
toc: FALSE
bibliography: references.bib
header-includes:
    - \usepackage{setspace}\doublespacing
abstract: "The projected global growth in population and incomes is expected to create pressure to convert forestland into farmland, with an estimated 144.2 million hectares of forestland estimated to be converted to agricultural land by 2033. At the same time, increasingly negative climate impacts are expected to generate further pressure to enhance the terrestrial carbon sink, but taking such actions would likely result in less agricultural output and higher food prices. Using the GTAP and GTM models, we model the impact of applying a tax on the value of output from land used in agricultural production and find that the net deforestation rate could be brought to zero for a relatively small cost. Results suggest that the well-being of global consumers would be reduced by $92.1 billion in 2033, which translates to a global average annual cost of $10.6 per person."
---

>>>>

---
title: "Avoiding global deforestation by taxing land in agricultural production: The implications for global markets"
date: "`r format(Sys.time(), '%B %d, %Y')`"
author: "Eric C. Davis, Maros Ivanic, and Brent Sohngen"
output: 
  bookdown::pdf_document2:
    keep_tex: TRUE
toc: FALSE
bibliography: references.bib
header-includes:
    - \usepackage{setspace}\doublespacing
abstract: "The projected global growth in population and incomes is expected to create pressure to convert forestland into farmland, with an estimated 144.2 million hectares of forestland estimated to be converted to agricultural land by 2033. At the same time, increasingly negative climate impacts are expected to generate further pressure to enhance the terrestrial carbon sink, but taking such actions would likely result in less agricultural output and higher food prices. Using the GTAP and GTM models, we model how different tax rates on the value of output from land used in agricultural production would impact deforestation. We find that, with a tax rate of zero percent on agricultural production, 144.2 million hectares (3.6%) of global forests would be converted to agricultural lands by 2033. With a 70 percent tax, however, the net deforestation rate would be brought to zero while the well-being of global consumers would be reduced by $92.1 billion in 2033, which translates to a global average annual cost of $10.6 per person."
---
